---
title: "HW-4"
author: "Jesse Grigolite"
date: "2023-05-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem #1

1.) 
Null Hypothesis: Fish length does not predict fish weight in trout perch.
H0: beta sub one = 0
Alternative Hypothesis: Fish length does predict fish weight in trout perch.
Ha: beta sub one does not = 0

2.) 
```{r, loading-libraries}
library(tidyverse)
library(here)
library(lterdatasampler)
library(performance)
library(broom)
library(flextable)
library(ggeffects)
library(car)
library(naniar)
```

```{r, load-data}
#read in data set
fish <- read.csv(here("data", "ntl6_v12.csv"))
```

```{r, filter-data}
#only focus in on the species trout perch
fish_data <- fish %>% 
  filter(spname == "TROUTPERCH")

```

b.)
```{r, visualize-missing-data}
#now visualzing missing data
gg_miss_var(fish_data) +
  #adding a caption
  labs(caption = "The above figure illustrates that there are 200 missing values for trout perch weight which will influence the sample size of our data.")
```
 
3.)
```{r, linear-model-fish}
#creating a linear model between predictor and response variables using the filtered data set
fish_model <- lm(weight ~ length, data = fish_data)

fish_model

```

4.)
```{r}
#first create a 2 by 2 grid and then visually check your assumptions
par(mfrow = c(2, 2))
plot(fish_model)
```

5.)
Residuals vs Fitted: This plot shows the constant variance of residuals, and appears to be randomly distributed about the red line and is fairly homoscedastic.
Normal Q-Q: This plot displays how normally distributed the residuals are. Based on the majority of the points following a linear trend this does appear to be normally distributed.
Scale Location: 
```{r}
dev.off()
```

